---
title: "Milestone 5: Final Project About Page and Cleaned Data"
author: Liz Masten
date: 10/18/2019
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning= FALSE, error= FALSE, message= FALSE)

library(readr)
library(readxl)
library(lubridate)
library(tidyverse)

conflict <- read_csv("1900-01-01-2019-10-17-Yemen.csv")
idp <- read_xlsx("idp.xlsx", skip = 1)
returnees <- read_xlsx("returnees.xlsx", skip = 1)

options(stringsAsFactors = FALSE)

```

```{r, echo = FALSE}

# Since the idp data start on 6/24/2019 and returnees data start on 7/1/2019, I dcided to start on 7/1/2019. I filtered the idp, returnee, and conflict data accordingly. 


conflict_dated <- conflict %>% 
      select("event_date", "event_type", "sub_event_type", "actor1", "admin2", "location", "latitude", "longitude", "fatalities") %>% 
      filter(event_date >= as.Date("2019-07-01"))

idp_dated <- idp %>% 
      select("District", "Sub-Area", "Total_#_of_HH", "Present_Location", "District_of_Origin", "Displacement_Date", "Return_reason", "Event_Description") %>% 
      filter(Displacement_Date >= as.Date("2019-07-01"))
  
returnees_dated <- returnees %>% 
      select("District", "Sub-Area", "Total_#_of_HH", "Present_Location", "District_of_Origin", "Return_Date", "Displacement/Return_reason", "Event_Description") %>%  
      filter(Return_Date >= as.Date("2019-07-01"))


      
```
```{r, plots}

#Exploratory data visualization: 

#These three plots are for metrics of conflict ONLY. 

#Plot of attacks (sub_event_type) that yielded at least 1 fatality for specified time period. 

event_type <- conflict_dated %>% 
  select(sub_event_type, fatalities) %>%  
  filter(fatalities >= 1)

ggplot(event_type, aes(x = sub_event_type, y = fatalities)) +
  geom_col() +
   theme(axis.text.x = element_text(angle = 90, hjust = 1))

#table of groups of actors (there are 52)

actor_grouped <- conflict_dated %>% 
  select(sub_event_type, actor1) %>% 
  group_by(actor1) %>% 
  summarise() 

#table of grouped sub event types 

event_grouped <- conflict_dated %>% 
  select(sub_event_type) %>% 
  group_by(sub_event_type) %>% 
  summarise()

# plot of attack types vs day 

day <- conflict_dated %>% 
  select(event_date, fatalities, sub_event_type) %>% 
  filter(fatalities >= 1)

ggplot(day, aes(x = event_date, y = fatalities)) + 
  geom_col()

```


# About 

### This site is designed to explore how conflict in Yemen shaped displacement flows from July to October 2019. 


# The Data 

### 1) The International Organization for Migration’s Displacement Tracking Matrix (IOM DTM) collects data on displacement and mobility. As of October 2019, they have tracked 28,542,792 displaced people. This site uses data from their collection on Yemen between 1 July 2019 and 8 October 2019. Please check out their work <a href="https://www.globaldtm.info/">here</a>. 


### 2) The Armed Conflict Location & Event Data (ACLED) Project is a “disaggregated data collection, analysis and crisis mapping project” that has collected an incredibly detailed account of political violence and protest events. This site uses data from their collection on Yemen between 1 July 2019 and 8 October 2019. Please check out their work <a href="https://www.acleddata.com/about-acled/">here</a>. 


# Connect 

### You can contact me at lizmasten@g.harvard.edu or connect with my on <a href="www.linkedin.com/in/elizabeth-masten-642567196">LinkedIn</a>. 
 

# Technical

### The source code for this site can be found at my <a href="https://github.com/LizMas/Milestone_5">GitHub</a>. 




